Android security updates

### 2014-02-11 QInF.tex
QInF: draft one year horizon

\section*{One year horizon}

>>>>

\section*{One year horizon}
\begin{itemize}
 \item A comprehensive database of root equivalent vulnerabilities affecting Android in a machine readable format on the website~\cite{androidvulnerabilities.org}.
 \item Comparison of different manufacturers to determine which is best at shipping updates for security vulnerabilities.
 \item Analysis of the behaviour of users with respect to Android updates -- how promptly do they get installed once made available.
 \item What else???
\end{itemize}
